Exploring the conformational dynamics of a large molecule in solution using an external electric field: A Nonequilibrium Molecular Dynamics Simulation

### 2013-08-27 writedown/npt-neq/alanine.tex
remove the stupid windows end-line symbol

To describe the system, we use a classical force field with TIP3P water model.
The EF is well know to be able to protonate the water molecule at the
intensity we used in the paper. However, this happens at the time
scale of femtosecond, which is much shorter than the slowest time
scale revolved by the current research, so on average it should not play an essential role on the conformational dynamics.
The polarization with respect to the external EF also does
not play a important role, because  under the EF of 1~V/nm, the induced dipole
of water is only c.a. 0.05~Debye that is negligible comparing with the
dipole moment response observed in our simulations.  Therefore, it is
reasonable to use a non-polarizable model in this study.  The reason we
prefer a rigid water model is that it is computationally more
efficient than any polarizable water model.  We also want to remind
the reader that it has been reported recently that the physical scale of the slowest 
dynamics differs in a considerable way between different force
fields~\cite{vitalini2013speed}. However, the qualitative conclusions (for
example the answer to the question of which is the slowest and the second slowest process, from which
conformation to which conformation the system moves) are basically consistent for the alanine from the point of view of force fields.

>>>>

To describe the system, we use a classical force field with TIP3P water model.
The EF is well know to be able to protonate the water molecule at the
intensity we used in the paper. However, this happens at the time
scale of femtoseconds, which is much shorter than the slowest time
scale resolved by the current research, so on average it should not play an essential role on the conformational dynamics.
The polarization with respect to the external EF also does
not play a important role, because  under the EF of 1~V/nm, the induced dipole
of water is only c.a. 0.05~Debye that is negligible comparing with the
dipole moment response observed in our simulations.  Therefore, it is
reasonable to use a non-polarizable model in this study.  The reason we
prefer a rigid water model is that it is computationally more
efficient than any polarizable water model.  We also want to remind
the reader that it has been reported recently that the physical scale of the slowest
dynamics differs in a considerable way between different force
fields~\cite{vitalini2013speed}. However, the qualitative conclusions (for
example the answer to the question of which is the slowest and the second slowest process, from which
conformation to which conformation the system moves) are basically consistent for the alanine from the point of view of force fields.
